The Astropy Project:

### 2017-09-29 main.tex
add todos
expand todos in coordinates

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, but now also local coordinates (via EarthLocation + Time)
    \item differential classes
    \item Proper motions, radial velocities
    \item JPL ephemerids
\end{itemize}

>>>>

\textbf{Key new features:}
\begin{itemize}
    \item TODO: Celestial coordinates, but now also local coordinates (via
    EarthLocation + Time). Now supports Alt-Az coordinates, observation planning
    - shoutout to astroplan
    \item TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.
    \item TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.
    \item TODO: JPL ephemerids % Who can write this? Erik?
\end{itemize}
